\Large{Holier Than Thou? No Partisan Gap in the Consumption\\ of Pornography Online}\footnote{You can download the replication materials from \href{http://github.com/soodoku/adult}{https://github.com/soodoku/adult}}

### 2023-01-04 ms/adult.tex
Update adult.tex

\thispagestyle{empty}
\begin{abstract}
\noindent Consumption of pornography has been blamed for a variety of societal ills, including the rise in misogyny, sex crimes, and the coarsening of culture. Using passively collected browsing data from YouGov, we investigate how much pornography Americans consume online. We find that there is a sharp positive skew in the consumption of pornography, with a small number of users consuming lots of pornography and most consuming small amounts. The median American Internet user today spends X minutes per month consuming pornography, visiting Y sites per month; the 95th percentile is X and Y respectively. Lastly, we find that, unlike previous research \citep{macinnis2015american, edelman2009markets}, which relied on ecological inference, Democrats consume about as much pornography online as Republicans.
\end{abstract} 
\clearpage
\setcounter{page}{1}
\doublespace

@@

In this paper, we investigate how much pornography Americans consume online. Using passive browsing data from YouGov, we find that there is a sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography. Most individuals in the sample do not consumer pornography.
The median American Internet user spends 0 minutes per month consuming pornography (0\% of their time online), visiting 122 unique sites. 
The median American consumer of pornography spends about 44 minutes per month consuming pornography (3\% of their time online), visiting three unique pornographic sites. 
The 95th percentile for time spent consuming pornography online is 337 minutes (about 21\% of their time online).

We also use the data to shed light on an age-old debate --- whether Democrats consume more pornography than Republicans or vice versa. Both parties claim the higher moral ground. And in surveys both parties think consumption of pornography is abhorrent, plausibly for different reasons. Unlike previous research, which relied on ecological inference, we find that Democrats consume about as much pornography online as Republicans \citep{macinnis2015american, edelman2009markets}. Adjusting for background attributes like age, gender etc., makes little difference.

@@

\subsection*{Consumption of Pornography}
The consumption of pornography is highly concentrated. Traffic to the top 10 most frequented porn sites is more than 12 times that of traffic to all other porn sites outside the top 10 (approximately 109 minutes vs 9 minutes, see \cref{fig:concentration_porn_consumption}). Close to 80 percent of the traffic to pornographic sites is concentrated in just one pornographic site, a behavior that is fairly consistent across parties (\cref{fig:concentration_porn_consumption_topX_by_party}). The next most frequented pornographic site constitutes less than 20 percent of total traffic.

The consumption of pornography online is also limited to a minority of respondents. Only about 32 percent of the respondents visited at least one pornography online during the sample period. The average consumer of pornography online spends approximately 230 minutes (standard deviation of 576 minutes), which is 10.6 percent of total browsing activity (standard deviation of 17.9 percent). These come from 233 visits to pornographic sites (standard deviation of 550), which is 6.9 percent of visits to all sites (standard deviation of 11.2 percent).

The key differences between consumers and non-consumers of pornography online are age and gender. Consumers of pornography online are younger and are more likely to be male.

@@

Our research has two major limitations. The first concern with our data is that we may not have data from all the machines that the respondent uses to visit online. If the respondent changes their behavior in response to the knowledge that their data is being collected (even if it is de-identified), for e.g., they may modify their behavior on the machine or figure out ways to evade detection, it may bias our results. In fact, we think it is likely that people would be less likely to search for pornography on machines on which they have installed passive monitoring software (though the data are de-identified). If that is so, our estimates are a lower bound of net consumption of pornography per machine. If this bias varies by party, our estimates of partisan differences will also be biased.

@@

>>>>

\thispagestyle{empty}
\begin{abstract}
\noindent Consumption of pornography has been blamed for a variety of societal ills, including the rise in misogyny, sex crimes, and the coarsening of culture. Using passively collected browsing data from YouGov, we investigate how much pornography Americans consume online. We find that there is a sharp positive skew in the consumption of pornography, with a small number of users consuming lots of pornography and most consuming small amounts. Only about 32 percent of the respondents consumed pornography online during the month long observation period. Of the people who consumed pornography, the median consumer spent about 44 minutes  consuming pornography and 95 percent spent less than 337 minutes. Lastly, we find that, unlike previous research \citep{macinnis2015american, edelman2009markets}, which relied on ecological inference, Democrats consume about as much pornography online as Republicans.
\end{abstract} 
\clearpage
\setcounter{page}{1}
\doublespace

@@

In this paper, we investigate how much pornography Americans consume online. Using passive browsing data from YouGov, we find that there is a sharp skew in the consumption of pornography, with a small set of users consuming a large chunk of pornography. About 68 percent of the respondents abstained from  pornography online during the month long observation period. Of the people who consumed pornography, the median consumer spent about 44 minutes consuming pornography and the 95th percentile consumer spent 337 minutes.

We also use the data to shed light on an age-old debate---whether Democrats consume more pornography than Republicans or vice versa. Both parties claim the higher moral ground. And in surveys both parties think consumption of pornography is abhorrent, plausibly for different reasons. Unlike previous research, which relied on ecological inference, we find that Democrats consume about as much pornography online as Republicans \citep{macinnis2015american, edelman2009markets}. Adjusting for background attributes like age, gender etc., makes little difference.

@@

\subsection*{Consumption of Pornography}
Only about 32 percent of the respondents consumed pornography online during the sample period. The average consumer of pornography online spent approximately 230 minutes (standard deviation of 576 minutes). The consumption of pornography was highly concentrated among a few sites with ten most frequented pornography sites receiving more than 12 times the traffic to all other porn sites  (approximately 109 minutes vs. 9 minutes, see \cref{fig:concentration_porn_consumption}). Close to 80 percent of the traffic to pornographic sites is concentrated in just one pornographic site. Looking at the characteristics of consumers of pornography, expectedly, consumers of pornography online are younger and are more likely to be male.

@@

Our research has three major limitations. The first concern with our data is that we may not have all the Internet visitation data from a user. If the respondent changes their behavior in response to the knowledge that their data is being collected (even if it is de-identified), for e.g., they may modify their behavior on the machine or figure out ways to evade detection, it may bias our results. In fact, we think it is likely that people would be less likely to search for pornography on machines on which they have installed passive monitoring software (though the data are de-identified). If that is so, our estimates are a lower bound of net consumption of pornography. If this bias varies by party, our estimates of partisan differences will also be biased.

@@

The third concern is that our measures are a point in time. We have data from one month in one year---June, 2022. It is possible that people consume less pornography online and instead spend time outside in June when the weather in many parts of the US is more pleasant than in preceding or following months.
